A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-11 manuscript.Rmd
add part about licences

>>>>

Even when other researchers are excited to use your code or materials, they are usually legally inhibited from to doing so.
That is because in many countries (i.e. the USA) the creator of something has exclusive right to use their creation.
A license allows other people to use what you have created.
<!---exact copy from our previous manuscript, do we need to change? -->
In our experience, the [Creative Commons - Attribution license (CC-BY)](https://creativecommons.org/licenses/by/4.0/) is often appropriate for sharing texts, R Markdown files, generated figures, and other media, whereas scripts and any other computer code are often best shared under the [MIT license](https://opensource.org/licenses/MIT) (or similar permissive licenses).
Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work.
These licenses are also in line with the recommendations by the Reproducible Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
A great resource to choose a license is [choosealicense.com](https://choosealicense.com), however, no resource, including our recommendation, replaces legal advice.
<!-- plagiary end -->
It is important to get written consent from collaborators when you change/add the license.
However, if they contribute to the project, after you have added a license, they give their consent by contributing.
To add a license to your project simply run:
